Capstone Movielens Report

### 2025-12-23 reports/capstone-movielens.site/02.4.UE-model.Rmd
Fix for report section: "UE Model"

@@

Finally, we add the *RMSE* value calculated for the *UE Model* to our *Result Table* and print the table using the following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L372):
```{r main-script@l372, eval=FALSE}
RMSEs.ResultTibble.UE <- RMSEs.ResultTibble.OMR |> 
  RMSEs.AddRow("UE Model", 
               edx.user_effect.RMSE,
               comment = "User Effect (UE) Model")
```
```{r}
RMSE_kable(RMSEs.ResultTibble.UE)
```

>>>>

::: {.noteblock data-latex=""}
In the code snippet above, we use the user-defined function [mse](#func.mse) described in the [Common Helper Functions]/[(Root) Mean Squared Error Calculation] section of [Appendix A](#appndx_a).
:::

@@

Finally, we add the *RMSE* value calculated for the *UE Model* to our *Result Table* and print the table using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L372):
```{r main-script@l372, eval=FALSE}
RMSEs.ResultTibble.UE <- RMSEs.ResultTibble.OMR |> 
  RMSEs.AddRow("UE Model", 
               edx.user_effect.RMSE,
               comment = "User Effect (UE) Model")
```
```{r}
RMSE_kable(RMSEs.ResultTibble.UE)
```
